---
title: "Lab 3"
author: "Kelsey McKenna"
date: "1/29/2019"
output: html_document
---

Team plot: The question we wish to answer is "How does gender impact health confidence?". 
This question is extremely interesting and important, because we are curious to see how gender impacts how healthy people are or how healthy people feel. 

Individual Plot:  Kelsey McKenna How does weight and height compare between genders?
I found that on average men are taller and heavier based on my graph which makes sense. Generally, women are less tall, but have more weight than men do for their height. 

```{r}
library(tidyverse)

source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)

ggplot(data=cdc) +
  geom_jitter(mapping = aes(x = weight, y = height, color= gender)) 

```



Individual Plot- Shreeya Basrur
Hypothesis: Is there a correlation between the what the respondents weighed and what they want to weigh? Does gender seem to have an impact on this correlation?


I, Shreeya Basrur, created a plot showing how current weight and ideal weight are related, and if gender impacts that correlation.The data showed that there is a positive correlation between these variables. As the weight of the responders increases, so does the desired weight described by the responders.This was true of both male and female responders, indicating that gender does not impact the relationship between current and ideal weight. I used the point geom function and adjusted the color of the points to reflect gender. 

In addition I used a position adjustment to make the scatterplot appear less crowded. I also added a line using the smooth geom to reflect the general trend of the correlation.

ggplot2::ggplot()
```{r}
ggplot(data = cdc) + 
  geom_point(mapping = aes(x = weight, y = wtdesire, color = gender, position = "jitter")) +
  geom_smooth(mapping = aes(x = weight, y = wtdesire)) +
  ggtitle("Desired Weight vs. Current Weight")
  xlab("Current Weight(lbs)")
  ylab("Desired Weight(lbs)")
  

```

Individual Plot - James Burke
Question: Is there a difference in the proportion of women who have smoked 100 times and the proportion of men who have smoked 100?

Hypothesis: If I had to guess I would say that more men have smoked 100 times than women, simply because I feel like most of the time I see people smoking, it is men.

I, James Burke, created a plot that compares the people who have smoked 100 times before and those who have not using the bar geom. I used the fill aestetic along with position_dodge() to show the different proportion of men and women in separate bars of different colors. The plot shows that the mojority have not smoked 100 times by about 1,000 people out of the 20,000 person sample. Of those who have smoked 100 times men are in the majority by about 500 people, so not by a lot. I also used the xlab/ylab layers to label the x (Response) and y (People) axis more accurately. Finally I labeled the tic marks of the x axis No and Yes, so it was more obvious what the respones were. To do so I also had to make the smoke100 variable a factor insteads of a continuous variable.

```{r}
library(tidyverse)
cdc <- as_tibble(cdc)
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = as.factor(smoke100), fill = gender), position = position_dodge()) +
  xlab("Response") +
  ylab("People") +
  scale_x_discrete(labels = c("No", "Yes"))
```
