---
title: "Lab 3"
author: "Kelsey McKenna"
date: "1/29/2019"
output: html_document
---
Team plot - Shreeya Basrur, Kelsey McKenna, Matthew Copeland, James Burke
Question: Based on the height and weight of an individual, as well as if they exercise. Does their desired weight differ between genders?
The idea behind the question is to see how self confidence in one's body vary based on their gender, their height and/or their weight in mind. 
Through looking at the data we can see that there is a cluster of data with varying blue and black dots, which suggests that a persons height and weight does not clearly affect how much they exercisd. But the line that flows through the cluster shows that generally females desired weight is lower than males which suggests that gender influences body confidence. Body confidence does not seem to be influenced by your body type or how much exercise, however based on the data female's body confidence may generally be lower based on their desired weight. Our best recomendation for this would be to take steps in society away from forcing the idealic women's body on females at all ages. This tends to skew what women desire to look like themselves, putting pressure on themselves to conform to that image. A concrete recommendation would be to start deversifying the representation of women in the media, so that females can see and look up to a more realistic figure.

What everybody did
Shreeya Basrur: Came up with the central question and created her plot that compares the current weight to the desired weight of males and females.
Kelsey McKenna: Wrote why the central question was so important and created her plot that compares the weight and height of men and women.
Matthew Copeland: Made the group plot and wrote the conclusion, along with his own plot relating general health to age.
James Burke: Added to the conclusion, made a recomendation and created his plot that compared the smoking habits of males and females.
```{r}
ggplot(data = cdc)+
  geom_point(aes(x = height,y = weight, color = exerany))+
  geom_smooth(aes(x = height, y = wtdesire, linetype = gender),color = "red")
```



Individual Plot:  Kelsey McKenna 
Question: How does weight and height compare between genders?
I found that on average men are taller and heavier based on my graph which makes sense. Generally, women are less tall, but have more weight than men do for their height. 

```{r}
library(tidyverse)

source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)

ggplot(data=cdc) +
  geom_jitter(mapping = aes(x = weight, y = height, color= gender)) +
  theme_dark()

```



Individual Plot- Shreeya Basrur
Hypothesis: Is there a correlation between the what the respondents weighed and what they want to weigh? Does gender seem to have an impact on this correlation?

I, Shreeya Basrur, created a plot showing how current weight and ideal weight are related, and if gender impacts that correlation.The data showed that there is a positive correlation between these variables. As the weight of the responders increases, so does the desired weight described by the responders.This was true of both male and female responders, indicating that gender does not impact the relationship between current and ideal weight. I used the point geom function and adjusted the color of the points to reflect gender. 

In addition I used a position adjustment to make the scatterplot appear less crowded. I also added a line using the smooth geom to reflect the general trend of the correlation.

ggplot2::ggplot()
```{r}
ggplot(data = cdc) + 
  geom_point(mapping = aes(x = weight, y = wtdesire, color = gender, position = "jitter")) +
  geom_smooth(mapping = aes(x = weight, y = wtdesire)) +
  ggtitle("Desired Weight vs. Current Weight")
  xlab("Current Weight(lbs)")
  ylab("Desired Weight(lbs)")
  

```



Individual Plot - James Burke
Question: Is there a difference in the proportion of women who have smoked 100 times and the proportion of men who have smoked 100?

Hypothesis: If I had to guess I would say that more men have smoked 100 times than women, simply because I feel like most of the time I see people smoking, it is men.

I, James Burke, created a plot that compares the people who have smoked 100 times before and those who have not using the bar geom. I used the fill aestetic along with position_dodge() to show the different proportion of men and women in separate bars of different colors. The plot shows that the mojority have not smoked 100 times by about 1,000 people out of the 20,000 person sample. Of those who have smoked 100 times men are in the majority by about 500 people, so not by a lot. I also used the xlab/ylab layers to label the x (Response) and y (People) axis more accurately. Finally I labeled the tic marks of the x axis No and Yes, so it was more obvious what the respones were. To do so I also had to make the smoke100 variable a factor insteads of a continuous variable.

```{r}
library(tidyverse)
cdc <- as_tibble(cdc)
ggplot(data = cdc) +
  geom_bar(mapping = aes(x = as.factor(smoke100), fill = gender), position = position_dodge()) +
  xlab("Whether they have smoked 100 times") +
  ylab("People") +
  scale_x_discrete(labels = c("No", "Yes"))+
  ggtitle("Male vs. Female Smokers") 
```



Individual Plot - Matthew Copeland 

Question: How does Age affect how you view your general health?
Hypothesis: The people who view they have better health are in the younger age gap of 20 and 30 year olds. 
I, Matthew Copeland, created a histogram to show the count of people based of their age. The x-axis describes the age and the y-axis describes the number of people in each age group in the study. The color of each bar represent the general health each person view their self as. The hight of each bar describe how many people view their general health relative to their age.

```{r}

ggplot(data = cdc)+
  geom_histogram(aes(x = age, fill = genhlth), position = "dodge",binwidth = 10)

```

